Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance

### 2019-05-21 Manuscript/manuscript.Rmd
Add Spiro and MD abstracts side-by-side
An introductory paragraph on resolution gap - purpose of study

# ABSTRACT

@@

>>>>

# ABSTRACT (Spiro version)

# ABSTRACT (MD version)

@@

[Paragraph about disconnect between Hi-C and epigenomic data] Despite the success of Hi-C technologies in revealing the high-order levels of genome organization (chromosome territories, A/B compartments, TADs, sub-TADs, chromatin loops), resolution of Hi-C data (~750kb [??? REF, Bonev 2017?]) remains well below resolution of epigenomic assays (hundredths of bases for ChIP-seq). This resolution gap between 1D and 3D genomic maps, as well as a paucity of chromatin features below the level of TADs, has significantly limited out understanding of epigenomic regulation of gene expression and its potential link to chromatin architecture. One aim of this study is to predict the location of TAD boundaries on a scale comparable to epigenomic assays. For this, we developed a model trained on a relaticely coarse Hi-C data for predicting 3D features (TAD boundaries) from 1D data (epigenomic datasets).
